Field training 02 - Leaf traits measurements

### 2023-06-12 submission_1/submission_1.qmd
restructures submissions
Also some tiny changes to the submissions

The aim of the vegetation sampling was to collect a random vegetation ground truth sample for 5x5 meter remote sensing imagery. On May 16th 2023, we recorded herbaceous vegetation on four subplots of 1x1 meter each ($1 \, \text{m}^2$) on the meadows of a small park named 'Kanonenteichanlage' between Liebigstraße and Brüderstraße in 04103 Leipzig, Germany. 
Firstly, we selected a homogeneous location without trees, shrubs or disturbances within a range of 20 meters. On that area, the location where a randomly thrown pile landed marked our central subplot. Secondly, we measured the coordinates of the relevé in LatLong/WGS84 format using a smartphone. Following, we recorded metadata as well as plant species abundance for the present herbaceous vegetation. The metadata includes a plot image, coverage of litter [%], soil [%], water [%] and moss [%] as well as the height. In order to assess the height, we measured the vertical extend from the base of the plant (soil level) to the tip of the highest point using a ruler, and excluding any aerial leaves or roots. This process was repeated several times (~20) for different species and the mean height calculated subsequently. For the remaining metadata, we calculated the mean of our personal/individual estimates (N = 6). Lastly, we identified all present species using the free software 'FloraIncognita' and the book 'Flora Vegetativa - Ein Bestimmungsbuch für Pflanzen der Schweiz im blütenlosen Zustand' (2020) by Eggenberg and Möhl. The cover fraction of each species was again calculated by taking the mean of our six individual estimates.
The same procedure was conducted for three more subplots arranged in 120° directions three meters from the center subplot.
Additionally, the recorded species cover fractions as well as the metadata of the four subplots was aggregated to a main plot using the mean of the four values, respectively.
Afterwards, the recorded data as well as the metadata as well as the aggregated data at the plot level were entered in GoogleDocs sheets, which can be see in Tables 1.1 and 1.2.

>>>>

The aim of the vegetation sampling was to collect a random vegetation ground truth sample for 5x5 meter remote sensing imagery. On May 16th 2023, we recorded herbaceous vegetation on four subplots of 1x1 meter each ($1 \, \text{m}^2$) on the meadows of a small park named 'Kanonenteichanlage' between Liebigstraße and Brüderstraße in 04103 Leipzig, Germany. 
Firstly, we selected a homogeneous location without trees, shrubs or disturbances within a range of 20 meters. On that area, the location where a randomly thrown pile landed marked our central subplot. Secondly, we measured the coordinates of the relevé in LatLong/WGS84 format using a smartphone. Following, we recorded metadata as well as plant species abundance for the present herbaceous vegetation. The metadata includes a plot image, coverage of litter [%], soil [%], water [%] and moss [%] as well as the height. In order to assess the height, we measured the vertical extend from the base of the plant (soil level) to the tip of the highest point using a ruler, and excluding any aerial leaves or roots. This process was repeated several times (~20) for different species and the mean height calculated subsequently. For the remaining metadata, we calculated the mean of our personal/individual estimates (N = 6). Lastly, we identified all present species using the free software 'FloraIncognita', 'PlantNet' and the book 'Flora Vegetativa - Ein Bestimmungsbuch für Pflanzen der Schweiz im blütenlosen Zustand' (2020) by Eggenberg and Möhl. The cover fraction of each species was again calculated by taking the mean of our six individual estimates.
The same procedure was conducted for three more subplots arranged in 120° directions three meters from the center subplot.
Additionally, the recorded species cover fractions as well as the metadata of the four subplots was aggregated to a main plot using the mean of the four values, respectively.
Afterwards, the recorded data as well as the metadata as well as the aggregated data at the plot level were entered in GoogleDocs sheets, which can be see in Tables 1.1 and 1.2.

### 2023-06-12 submission_2/submission_2.qmd
restructures submissions
Also some tiny changes to the submissions

In the next step, we determined the mass per leaf area. We took the sheets out of the paper bag and placed them one by one into the sheet scanner. We had to make sure that the sheets were fully spread out, did not overlap, and were within the measurement range area. For some sheets, the scanner was not large enough to measure all 10 sheets at once. So we did multiple scans and added up and documented the measured leaf area for each species.

@@

For this approach we took Photos of single or multiple leafs on one (or two) A4 papers. 
These photos were then preprocessed with the image-software `gimp` and then calculated the leaf size with a [python script](https://github.com/yum-yab/ground_truthing_module/blob/main/leaf_area_measure/leaf_area_measurement.py).

@@

The code and the description how to use it can be found in [this git repository](https://github.com/yum-yab/ground_truthing_module/blob/main/leaf_area_measure/). 
Here we will only describe the main ideas of the process. 
In general we know the area of the A4 paper, so to determine leaf size we only need to know the number of `leaf-pixels` in relation to `leaf-pixels + paper-pixels` and therefor we can calculate the area of the leaf. 
Unfortunately shadows of not fully flat leaves can add a lot of noise to the trivial approach (converting it to greyscale and cutting at a certain threshold). 
To fix this we transposed the image in the `HSV` color space, where all grey/white colors have a very low saturation value (compared to the green leaves), so we determine a  saturation threshold here (a comparison feature between Bitmask, `HSV` and original image was implemented to find a fitting value) and generate the bitmask in this way.
The transparent parts are not considered during the area calculation, only the white (paper), grey (shadows, counted as paper) and green (leaf) pixels.

>>>>

In the next step, we determined the mass per leaf area.
For this task two different methods were used: A specialized scanner for this exact purpose and a python script calculating the leaf area based of photos on an a DIN-A4 paper.

## Specialized Scanner

 We took the sheets out of the paper bag and placed them one by one into the sheet scanner. We had to make sure that the sheets were fully spread out, did not overlap, and were within the measurement range area. For some sheets, the scanner was not large enough to measure all 10 sheets at once. So we did multiple scans and added up and documented the measured leaf area for each species.

@@

For this approach we took Photos of single or multiple leafs on one (or two) A4 papers. 
These photos were then preprocessed with the image-software `gimp` and then calculated the leaf size with a [python script](https://github.com/yum-yab/ground_truthing_module/blob/main/leaf_area_measure/leaf_area_measurement.py).
The photos (unprocessed and otherwise) can be found [here](https://github.com/yum-yab/ground_truthing_module/tree/main/leaf_area_measure/leaf_images)

@@

The code and the description how to use it can be found in [this git repository](https://github.com/yum-yab/ground_truthing_module/blob/main/leaf_area_measure/). 
Here we will only describe the main ideas of the process. 
Since we know the area of the A4 paper, to determine leaf size we only need to know the number of `leaf-pixels` in relation to `leaf-pixels + paper-pixels` ($\equiv$ DIN-A4) and therefor we can calculate the area of the leaf. 
Unfortunately shadows of not fully flat leaves can add a lot of noise to the trivial approach (converting it to greyscale and cutting at a certain threshold). 
To fix this we transposed the image in the `HSV` color space, where all grey/white colors have a very low saturation value (compared to the green leaves), so we determine a  saturation threshold here (a comparison feature between Bitmask, `HSV` and original image was implemented to find a fitting value) and generate the bitmask in this way.
The transparent parts are not considered during the area calculation, only the white (paper), grey (shadows, counted as paper) and green (leaf) pixels.
